\documentclass[a4paper, UTF8]{article}
\usepackage{neurips_2025}
\usepackage{amsmath, amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

\theoremstyle{plain}
\newtheorem{theorem}{\indent Theorem}[section]
\newtheorem{lemma}[theorem]{\indent Lemma}
\newtheorem{assumption}{\indent Assumption}[section]
\newtheorem{note}[theorem]{\indent Notation}
\newtheorem{proposition}[theorem]{\indent Proposition}
\newtheorem{corollary}[theorem]{\indent Corollary}
\newtheorem{definition}{\indent Definition}[section]
\newtheorem{example}{\indent Example}[section]
\newtheorem{remark}{\indent Remark}[section]
\newenvironment{solution}{\begin{proof}[\indent\bf Solution]}{\end{proof}}
\renewcommand{\proofname}{\indent\bf Proof}

\title{\bf{Information Exposure Maximization in Social Networks: A Comparative Study of Monte Carlo-Guided Heuristics and Evolutionary Algorithms}}

\author{\bf{Yanqiao Chen}\\
        Department of Computer Science\\
        Southern University of Science and Technology\\
        \texttt{12412115@mail.sustech.edu.cn}}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
The Information Exposure Maximization Problem (IEMP) in social networks presents significant computational challenges due to its NP-hard nature and the stochastic characteristics of information propagation. This report presents a comprehensive comparative analysis of two distinct algorithmic approaches for solving the IEMP: a Monte Carlo-guided heuristic algorithm that combines IMRank-based candidate screening with precise Monte Carlo evaluation, and a pure evolutionary algorithm employing binary encoding with penalty-based constraint handling. Through extensive experimentation on three test cases of varying scales, we demonstrate that the MC-guided heuristic consistently achieves superior performance with full budget utilization, while the genetic algorithm, despite passing all baseline requirements, exhibits substantial inefficiencies in budget exploitation. Our analysis reveals that the combination of fast heuristic screening and accurate Monte Carlo evaluation provides an effective paradigm for addressing complex influence maximization problems in large-scale social networks.
\end{abstract}

\section{Introduction}\label{sec:intro}

The proliferation of social media platforms has fundamentally transformed how information propagates through society, creating unprecedented opportunities for targeted information dissemination and influence maximization. In this context, the Information Exposure Maximization Problem (IEMP) emerges as a critical computational challenge that seeks to optimize the distribution of information across networked populations. Unlike traditional influence maximization problems that focus solely on maximizing the spread of a single campaign, the IEMP addresses the more nuanced scenario of managing two competing or complementary information campaigns simultaneously, with the objective of maximizing the expected number of network nodes that achieve balanced exposure---defined as being exposed to either both campaigns or neither campaign.

The mathematical formulation of the IEMP presents several significant computational challenges that render exact solution approaches infeasible for practical network sizes. First, the problem inherits the NP-hard complexity characteristics of traditional influence maximization problems, meaning that finding the optimal seed set requires evaluating an exponentially large search space. Second, the stochastic nature of information propagation under the Independent Cascade (IC) model introduces additional complexity, as the objective function must be estimated through computationally expensive Monte Carlo simulations. Third, the balanced exposure objective introduces an additional layer of complexity beyond simple coverage maximization, as it requires considering the symmetric difference between the reach sets of two campaigns rather than merely maximizing the union of their influences.

Given these computational challenges, the development of efficient approximation algorithms becomes essential for addressing real-world instances of the IEMP. This report presents a comprehensive comparative analysis of two distinct algorithmic paradigms for solving the IEMP. The first approach, which we term the Monte Carlo-guided heuristic algorithm, combines the computational efficiency of heuristic screening methods with the accuracy of Monte Carlo simulation for candidate evaluation. Specifically, this approach employs the IMRank algorithm for generating high-quality candidate pools and uses Monte Carlo simulation to guide a greedy selection process, thereby correcting the estimation biases inherent in purely heuristic approaches while maintaining computational tractability.

The second approach implements a pure evolutionary algorithm based on genetic algorithm principles. This method employs binary chromosome encoding to represent candidate solutions, with each chromosome encoding membership in the two seed sets $S_1$ and $S_2$. The algorithm utilizes penalty-based constraint handling to manage the budget constraint and employs standard genetic operators including uniform crossover and bit-flip mutation. By maintaining a population of candidate solutions and iteratively evolving this population through selection, crossover, and mutation operations, the genetic algorithm seeks to discover high-quality solutions through global search.

The remainder of this report is organized as follows. Section \ref{sec:problem} provides a formal mathematical formulation of the IEMP and establishes the necessary theoretical foundations. Section \ref{sec:heuristic} presents a detailed exposition of the MC-guided heuristic algorithm, including its theoretical underpinnings and algorithmic implementation. Section \ref{sec:genetic} describes the genetic algorithm approach, detailing its encoding scheme, fitness function, and evolutionary operators. Section \ref{sec:experiments} presents comprehensive experimental results comparing the performance of both algorithms across three test cases of varying scales. Section \ref{sec:analysis} provides an in-depth analysis of the results, examining factors such as budget utilization, solution quality, and algorithmic efficiency. Finally, Section \ref{sec:conclusion} summarizes our findings and discusses directions for future research.

\section{Problem Formulation and Preliminaries}\label{sec:problem}

\subsection{Mathematical Definition of the IEMP}

The Information Exposure Maximization Problem can be formally defined within the framework of graph theory and probabilistic propagation models. Consider a social network represented as a directed graph $G = (V, E)$, where the vertex set $V = \{v_1, v_2, \ldots, v_n\}$ represents the individuals in the network and the edge set $E \subseteq V \times V$ represents the social connections between them. Each directed edge $(u, v) \in E$ is associated with two propagation probabilities $p_1(u, v)$ and $p_2(u, v)$, representing the probabilities that information from campaign 1 and campaign 2, respectively, propagates from node $u$ to node $v$.

\begin{definition}[Information Exposure Maximization Problem]
Given the social network graph $G = (V, E)$ with propagation probabilities, two initial seed sets $I_1, I_2 \subseteq V$ for campaigns 1 and 2 respectively, and a budget constraint $k \in \mathbb{Z}^+$, the Information Exposure Maximization Problem seeks to find two additional seed sets $S_1, S_2 \subseteq V \setminus (I_1 \cup I_2)$ satisfying $|S_1| + |S_2| \leq k$ that maximize the expected balanced information exposure:
\begin{equation}\label{eq:objective}
\sigma(S_1, S_2) = \mathbb{E}\left[|V \setminus (r(S_1 \cup I_1) \Delta r(S_2 \cup I_2))|\right]
\end{equation}
where $r(S)$ denotes the set of nodes reached by a campaign with seed set $S$ under the Independent Cascade model, and $\Delta$ denotes the symmetric difference between two sets.
\end{definition}

The objective function $\sigma(S_1, S_2)$ counts the expected number of nodes that are either exposed to both campaigns (in the intersection of the reach sets) or exposed to neither campaign (in the complement of the union of reach sets). This formulation captures the essence of balanced exposure by penalizing nodes that are exposed to exactly one campaign, which corresponds to the symmetric difference $r(S_1 \cup I_1) \Delta r(S_2 \cup I_2)$.

\subsection{The Independent Cascade Model with Dual Campaigns}

The propagation dynamics in the IEMP are governed by a dual-campaign variant of the Independent Cascade (IC) model. Under this model, information propagation proceeds in discrete time steps, with each campaign evolving independently according to its own propagation probabilities. At time $t = 0$, all nodes in the seed sets $I_1 \cup S_1$ (for campaign 1) and $I_2 \cup S_2$ (for campaign 2) become active for their respective campaigns.

At each subsequent time step $t > 0$, each node $u$ that became active in the previous time step $t-1$ attempts to activate each of its inactive neighbors $v$ with the corresponding campaign's propagation probability. Specifically, for campaign $c \in \{1, 2\}$, node $u$ attempts to activate neighbor $v$ with probability $p_c(u, v)$. If the activation is successful, $v$ becomes active for campaign $c$ at time $t$ and will attempt to propagate the campaign further in subsequent steps. Each activation attempt is independent, and each node has only one chance to activate each neighbor per campaign.

The propagation process terminates when no new activations occur in a time step. At this point, we define the reach set $r_c$ for each campaign $c$ as the set of all nodes that were either seed nodes for that campaign or were successfully activated during the propagation process.

\subsection{Computational Complexity and Approximation Challenges}

The IEMP inherits the computational complexity characteristics of traditional influence maximization problems, which have been extensively studied in the literature. Specifically, the problem of maximizing influence spread under the IC model has been proven to be NP-hard, and the objective function is submodular but not necessarily monotone. These complexity results extend to the IEMP, as the traditional influence maximization problem can be reduced to a special case of the IEMP by setting one campaign's seed set to empty.

The computational challenges are further exacerbated by the need to estimate the expected value in Equation \eqref{eq:objective}. Unlike deterministic optimization problems where the objective function can be evaluated exactly, the stochastic nature of the IC model requires Monte Carlo simulation to estimate the expected reach sets. Each simulation involves running the propagation process multiple times and averaging the results, which is computationally expensive, particularly for large networks where each simulation may require simulating propagation through thousands of nodes and edges.

Given these computational challenges, exact solution approaches are infeasible for all but the smallest network instances. Consequently, the development of efficient approximation algorithms that can discover high-quality solutions within reasonable computational time becomes essential. The approximation algorithms presented in this report--- the MC-guided heuristic and the genetic algorithm--- represent two distinct paradigms for addressing these computational challenges.

\section{Monte Carlo-Guided Heuristic Algorithm}\label{sec:heuristic}

\subsection{Algorithmic Overview and Design Philosophy}

The Monte Carlo-guided heuristic algorithm represents a hybrid approach that combines the computational efficiency of heuristic screening with the accuracy of Monte Carlo simulation for precise evaluation. The fundamental insight underlying this approach is that purely heuristic methods, while computationally efficient, often suffer from estimation biases when approximating influence spread, particularly in large networks where the propagation dynamics are complex. Conversely, pure Monte Carlo methods, while accurate, are computationally prohibitive when evaluating a large number of candidate solutions.

Our approach bridges this gap by employing a two-stage process. In the first stage, we utilize the IMRank algorithm to rapidly generate a high-quality candidate pool of limited size, thereby reducing the search space from potentially thousands of nodes to a manageable number (typically 100-150 candidates). In the second stage, we employ Monte Carlo simulation to precisely evaluate the marginal contribution of each candidate node, thereby guiding a greedy selection process that constructs the solution incrementally.

The design philosophy behind this approach draws upon the rich literature on influence maximization heuristics, particularly the IMRank algorithm which has demonstrated effectiveness in identifying influential nodes through self-consistent ranking. By combining IMRank's screening capability with Monte Carlo's evaluation accuracy, we achieve a balance between solution quality and computational efficiency that is essential for addressing large-scale instances of the IEMP.

\subsection{IMRank-Based Candidate Pool Generation}

The IMRank algorithm forms the foundation of our candidate generation process. IMRank operates on the principle of self-consistent ranking, wherein nodes are iteratively ranked based on their estimated influence, with the ranking itself informing the influence estimation. This self-referential approach captures the recursive nature of influence propagation in social networks, where a node's influence depends not only on its direct connections but also on the influence of its neighbors.

The algorithm begins by computing an initial ranking based on weighted out-degree. For each campaign $c \in \{1, 2\}$, the weighted degree of node $v$ is computed as $d_c(v) = \sum_{(v, u) \in E} p_c(v, u)$. Nodes are then ranked in descending order of their weighted degrees, with ties broken by total out-degree and node identifier.

Following initialization, the algorithm enters an iterative refinement phase. In each iteration, the algorithm applies the Last-to-First Allocating (LFA) strategy to compute influence scores for all nodes based on the current ranking. The LFA strategy processes nodes in reverse order of their current ranking (from lowest to highest), propagating influence estimates from lower-ranked nodes to their higher-ranked neighbors. This propagation follows the intuition that influence flows from less influential nodes to more influential nodes in the ranking.

Specifically, for each node $v$ processed in reverse order, the algorithm distributes its current influence mass $M[v]$ to its parents (nodes with edges pointing to $v$) that have higher rankings. For each such parent $u$ with ranking position $r(u) < r(v)$, the influence contribution is computed as $M[u] \mathrel{+}= M[v] \cdot p_c(v, u)$, and the remaining mass at $v$ is updated as $M[v] \mathrel{*}= (1 - p_c(v, u))$. This process continues until all higher-ranked parents have been considered or the remaining mass falls below a threshold.

After applying the LFA strategy, nodes are re-ranked based on their computed influence scores $M[v]$. The algorithm iterates this process of LFA computation and re-ranking until convergence, defined as the ranking remaining unchanged between consecutive iterations, or until a maximum iteration count is reached. The converged ranking provides a self-consistent ordering of nodes by influence, which is then used to select the top candidates for the Monte Carlo evaluation stage.

\begin{algorithm}[htbp]
\caption{IMRank Self-Consistent Ranking}
\label{alg:imrank}
\begin{algorithmic}[1]
\Require Graph $G = (V, E)$, propagation probabilities $\{p_c(u,v)\}$, campaign $c$, max iterations $T$
\Ensure Self-consistent ranking $\pi$ and influence scores $M$
\State Initialize ranking $\pi_0$ by weighted out-degree: $\pi_0(v) \leftarrow \sum_{(v,u) \in E} p_c(v,u)$
\For{$t = 1$ to $T$}
    \State Initialize $M[v] \leftarrow 1$ for all $v \in V$
    \For{$v$ in reverse order of $\pi_{t-1}$}
        \State $\text{remaining} \leftarrow M[v]$
        \For{each parent $u$ of $v$ with $\pi_{t-1}(u) < \pi_{t-1}(v)$}
            \State $p \leftarrow p_c(u, v)$
            \State $M[u] \leftarrow M[u] + \text{remaining} \cdot p$
            \State $\text{remaining} \leftarrow \text{remaining} \cdot (1 - p)$
            \If{$\text{remaining} < \epsilon$}
                \State \textbf{break}
            \EndIf
        \EndFor
    \EndFor
    \State Create new ranking $\pi_t$ by sorting $V$ descending by $M[v]$
    \If{$\pi_t = \pi_{t-1}$}
        \State \textbf{return} $\pi_t, M$
    \EndIf
\EndFor
\State \textbf{return} $\pi_T, M$
\end{algorithmic}
\end{algorithm}

\subsection{Monte Carlo-Guided Greedy Selection}

With the candidate pool generated by IMRank, the algorithm proceeds to the Monte Carlo-guided greedy selection phase. This phase constructs the solution sets $S_1$ and $S_2$ incrementally over $k$ iterations, where $k$ is the budget constraint. At each iteration, the algorithm evaluates the marginal contribution of adding each candidate node to either $S_1$ or $S_2$, using Monte Carlo simulation to obtain precise estimates of the objective function improvement.

The greedy selection process operates as follows. Let $V_{\text{avail}}$ denote the set of available nodes not in the initial seed sets $I_1 \cup I_2$, and let $C \subseteq V_{\text{avail}}$ denote the candidate pool of size $N$ generated by IMRank. Starting with empty sets $S_1 = S_2 = \emptyset$, the algorithm iterates for $i = 1$ to $k$:

For each candidate node $v \in C \setminus (S_1 \cup S_2)$, the algorithm evaluates two potential moves: (1) adding $v$ to $S_1$, and (2) adding $v$ to $S_2$. For each move, the algorithm runs $M$ Monte Carlo simulations of the IC propagation process, where $M$ is a parameter controlling the trade-off between evaluation accuracy and computational cost. Each simulation computes the objective function value $\sigma(S_1 \cup \{v\}, S_2)$ or $\sigma(S_1, S_2 \cup \{v\})$ by simulating the propagation of both campaigns and computing the size of the complement of the symmetric difference of the reach sets.

The marginal gain for adding $v$ to $S_1$ is computed as $\Delta_1(v) = \sigma(S_1 \cup \{v\}, S_2) - \sigma(S_1, S_2)$, and similarly for adding to $S_2$ as $\Delta_2(v) = \sigma(S_1, S_2 \cup \{v\}) - \sigma(S_1, S_2)$. The algorithm selects the candidate $v^*$ and campaign $c^* \in \{1, 2\}$ that maximize the marginal gain, and updates the corresponding solution set $S_{c^*} \leftarrow S_{c^*} \cup \{v^*\}$.

\begin{algorithm}[htbp]
\caption{Monte Carlo-Guided Greedy Selection}
\label{alg:mc-greedy}
\begin{algorithmic}[1]
\Require Candidate pool $C$, initial sets $I_1, I_2$, budget $k$, MC simulations $M$
\Ensure Solution sets $S_1, S_2$
\State $S_1 \leftarrow \emptyset$, $S_2 \leftarrow \emptyset$
\For{$i = 1$ to $k$}
    \State $\text{best\_gain} \leftarrow -\infty$, $\text{best\_node} \leftarrow \text{null}$, $\text{best\_campaign} \leftarrow 1$
    \For{each $v \in C \setminus (S_1 \cup S_2)$}
        \State $\sigma_1 \leftarrow \text{MonteCarloEvaluate}(S_1 \cup \{v\}, S_2, I_1, I_2, M)$
        \State $\Delta_1 \leftarrow \sigma_1 - \sigma(S_1, S_2)$
        \If{$\Delta_1 > \text{best\_gain}$}
            \State $\text{best\_gain} \leftarrow \Delta_1$, $\text{best\_node} \leftarrow v$, $\text{best\_campaign} \leftarrow 1$
        \EndIf
        \State $\sigma_2 \leftarrow \text{MonteCarloEvaluate}(S_1, S_2 \cup \{v\}, I_1, I_2, M)$
        \State $\Delta_2 \leftarrow \sigma_2 - \sigma(S_1, S_2)$
        \If{$\Delta_2 > \text{best\_gain}$}
            \State $\text{best\_gain} \leftarrow \Delta_2$, $\text{best\_node} \leftarrow v$, $\text{best\_campaign} \leftarrow 2$
        \EndIf
    \EndFor
    \If{$\text{best\_campaign} = 1$}
        \State $S_1 \leftarrow S_1 \cup \{\text{best\_node}\}$
    \Else
        \State $S_2 \leftarrow S_2 \cup \{\text{best\_node}\}$
    \EndIf
\EndFor
\State \textbf{return} $S_1, S_2$
\end{algorithmic}
\end{algorithm}

The Monte Carlo evaluation function operates by running $M$ independent simulations of the IC propagation process. In each simulation, the algorithm initializes the active sets for both campaigns as the union of their respective initial and selected seed sets, then iteratively propagates activation through the network according to the propagation probabilities until no new activations occur. The reach set for each campaign is recorded as the set of all nodes that were either seeds or were successfully activated. The objective function value for that simulation is computed as the total number of nodes minus the size of the symmetric difference of the two reach sets. The final estimate is the average of these values across all $M$ simulations.

\subsection{Theoretical Properties and Computational Complexity}

The MC-guided heuristic algorithm combines the submodularity properties of the influence maximization objective with the variance reduction benefits of Monte Carlo estimation. While the greedy selection process does not provide the theoretical $(1 - 1/e)$ approximation guarantee of the standard greedy algorithm for submodular maximization (due to the use of Monte Carlo estimates rather than exact function evaluations), empirical results demonstrate that the algorithm achieves high-quality solutions in practice.

The computational complexity of the algorithm is dominated by the Monte Carlo evaluation phase. Each Monte Carlo simulation requires $O(|E|)$ time in the worst case, as each edge may be traversed during the propagation process. With $M$ simulations per evaluation, and evaluating $O(|C|)$ candidates for $k$ iterations, the total complexity is $O(k \cdot |C| \cdot M \cdot |E|)$. By limiting the candidate pool $|C|$ to a constant (e.g., 100-150 nodes) through IMRank screening, the algorithm achieves practical runtime even for large networks.

\section{Genetic Algorithm Approach}\label{sec:genetic}

\subsection{Evolutionary Computing Paradigm for IEMP}

The genetic algorithm approach to the IEMP represents a fundamentally different paradigm from the heuristic method, employing principles of evolutionary computing to search the solution space through population-based optimization. Rather than constructing a solution incrementally through greedy selection, the genetic algorithm maintains a population of candidate solutions that evolves over generations through the application of selection, crossover, and mutation operators. This population-based approach offers the potential for global exploration of the search space, potentially discovering solutions that might be missed by local search heuristics.

The design of our genetic algorithm follows the canonical structure of evolutionary algorithms while incorporating problem-specific adaptations for the IEMP. Key design decisions include the choice of binary chromosome encoding to represent membership in the two seed sets, the development of a penalty-based fitness function to handle the budget constraint, and the implementation of two-phase Monte Carlo evaluation to balance accuracy and computational efficiency during the evolutionary process.

\subsection{Binary Chromosome Encoding Scheme}

The representation of candidate solutions in the genetic algorithm employs a binary chromosome encoding scheme that directly captures membership in the two seed sets $S_1$ and $S_2$. Given the set of available nodes $V_{\text{avail}} = V \setminus (I_1 \cup I_2)$, we assign an index to each available node, creating a mapping from indices $\{0, 1, \ldots, n_{\text{avail}} - 1\}$ to nodes in $V_{\text{avail}}$. The chromosome is then defined as a binary string of length $2 \times n_{\text{avail}}$, where the first $n_{\text{avail}}$ bits encode membership in $S_1$ and the remaining $n_{\text{avail}}$ bits encode membership in $S_2$.

Specifically, for a chromosome $\mathbf{x} = (x_0, x_1, \ldots, x_{2n_{\text{avail}}-1})$, the decoding function extracts the seed sets as follows:
\begin{align}
S_1(\mathbf{x}) &= \{v_i \in V_{\text{avail}} : x_i = 1, 0 \leq i < n_{\text{avail}}\} \\
S_2(\mathbf{x}) &= \{v_{i-n_{\text{avail}}} \in V_{\text{avail}} : x_i = 1, n_{\text{avail}} \leq i < 2n_{\text{avail}}\}
\end{align}

This encoding scheme has several advantages for the IEMP. First, it naturally handles the constraint that nodes cannot be selected from the initial seed sets, as these nodes are excluded from the encoding. Second, it allows for arbitrary combinations of $S_1$ and $S_2$ memberships, subject to the budget constraint. Third, the binary representation is amenable to standard genetic operators such as crossover and mutation.

However, the encoding also allows for invalid solutions where a node is selected for both $S_1$ and $S_2$ simultaneously (corresponding to both $x_i = 1$ and $x_{i+n_{\text{avail}}} = 1$ for some $i$), or where the total number of selected nodes exceeds the budget $k$. These violations are handled through the fitness function's penalty mechanism, as described in the following section.

\subsection{Penalty-Based Fitness Function}

The fitness function in our genetic algorithm serves the dual purpose of evaluating solution quality and enforcing constraints. Unlike the heuristic algorithm, which maintains feasibility by construction, the genetic algorithm allows infeasible solutions to exist in the population but penalizes them to reduce their reproductive success.

The fitness function is defined as follows. Let $\mathbf{x}$ be a chromosome decoding to sets $(S_1, S_2)$, and let $b = |S_1| + |S_2|$ be the total number of selected nodes. If $b \leq k$ (feasible solution), the fitness is computed as the Monte Carlo estimate of the objective function:
\begin{equation}
f(\mathbf{x}) = \text{MonteCarlo}(S_1, S_2, M_{\text{coarse}})
\end{equation}

If $b > k$ (infeasible solution), the fitness is assigned a penalty value proportional to the constraint violation:
\begin{equation}
f(\mathbf{x}) = -b
\end{equation}

This penalty scheme ensures that infeasible solutions have negative fitness values, making them unlikely to be selected for reproduction. The magnitude of the penalty increases with the severity of the violation, providing stronger discouragement for solutions that greatly exceed the budget.

Additionally, we incorporate a budget usage bonus to encourage fuller utilization of the available budget within feasible solutions. The modified fitness function for feasible solutions becomes:
\begin{equation}
f(\mathbf{x}) = \text{MonteCarlo}(S_1, S_2, M_{\text{coarse}}) + \lambda \cdot \frac{b}{k}
\end{equation}
where $\lambda$ is a small constant (e.g., 0.5) controlling the strength of the bonus. This bonus term provides a slight advantage to solutions that use more of their budget, countering the tendency of the genetic algorithm to evolve sparse solutions.

\begin{algorithm}[htbp]
\caption{Fitness Evaluation with Penalty and Bonus}
\label{alg:fitness}
\begin{algorithmic}[1]
\Require Chromosome $\mathbf{x}$, decoded sets $S_1, S_2$, budget $k$, MC simulations $M$, bonus weight $\lambda$
\Ensure Fitness value $f$
\State $b \leftarrow |S_1| + |S_2|$
\If{$b > k$}
    \State $f \leftarrow -b$ \Comment{Penalty for infeasibility}
\Else
    \State $\sigma \leftarrow \text{MonteCarlo}(S_1, S_2, M)$
    \State $f \leftarrow \sigma + \lambda \cdot (b / k)$ \Comment{Score plus budget bonus}
\EndIf
\State \textbf{return} $f$
\end{algorithmic}
\end{algorithm}

\subsection{Population Initialization and Genetic Operators}

The initial population is generated through a combination of random initialization and degree-biased initialization. For random initialization, each bit in each chromosome is set to 1 with probability proportional to the target sparsity, typically chosen such that the expected number of selected nodes is $k/2$ to ensure initial feasibility. For degree-biased initialization, nodes with higher out-degrees have increased probability of being selected, providing a heuristic boost to the initial population quality.

The genetic operators employed in our algorithm include uniform crossover and bit-flip mutation. Uniform crossover operates by independently selecting each bit of the offspring from one of the two parents with equal probability. Given parent chromosomes $\mathbf{x}$ and $\mathbf{y}$, the offspring $\mathbf{z}$ is generated as:
\begin{equation}
z_i = \begin{cases}
x_i & \text{with probability } 0.5 \\
y_i & \text{with probability } 0.5
\end{cases}
\end{equation}

Bit-flip mutation operates by flipping each bit in the chromosome with a small probability $p_m$ (typically 0.05). For each bit $x_i$:
\begin{equation}
x_i \leftarrow \begin{cases}
1 - x_i & \text{with probability } p_m \\
x_i & \text{with probability } 1 - p_m
\end{cases}
\end{equation}

Selection is performed using tournament selection with tournament size 3. In each selection operation, 3 individuals are randomly sampled from the population, and the individual with the highest fitness is selected as a parent. This selection mechanism provides selection pressure while maintaining population diversity.

Elitism is employed to preserve the best individuals across generations. The top $E$ individuals (typically 2) from the current generation are directly copied to the next generation without modification, ensuring that high-quality solutions are not lost due to the stochastic nature of crossover and mutation.

\subsection{Two-Phase Monte Carlo Evaluation}

To balance the trade-off between evaluation accuracy and computational efficiency during evolution, our genetic algorithm employs a two-phase Monte Carlo evaluation strategy. During the evolutionary process, when evaluating the fitness of individuals in the population, we use a coarse evaluation with a smaller number of Monte Carlo simulations $M_{\text{coarse}}$ (typically 30). This provides a relatively fast estimate that is sufficient for guiding the evolutionary search.

After the evolutionary process terminates, we perform a fine evaluation of the best individual using a larger number of simulations $M_{\text{fine}}$ (typically 200-500). This provides a more accurate estimate of the solution quality for final reporting.

The evolutionary process terminates when either the maximum number of generations is reached or when no improvement has been observed for a specified number of consecutive generations (early stopping criterion).

\begin{algorithm}[htbp]
\caption{Genetic Algorithm for IEMP}
\label{alg:genetic}
\begin{algorithmic}[1]
\Require Available nodes $V_{\text{avail}}$, budget $k$, population size $P$, generations $G$, elite count $E$
\Ensure Best solution $(S_1^*, S_2^*)$
\State Initialize population $\mathcal{P}$ with $P$ individuals
\State Evaluate fitness of all individuals using $M_{\text{coarse}}$
\For{$g = 1$ to $G$}
    \State Sort $\mathcal{P}$ by fitness descending
    \State $\mathcal{P}_{\text{new}} \leftarrow \text{top } E \text{ individuals from } \mathcal{P}$ \Comment{Elitism}
    \While{$|\mathcal{P}_{\text{new}}| < P$}
        \State Select parents $p_1, p_2$ using tournament selection
        \State Generate offspring $c_1, c_2$ via uniform crossover
        \State Apply bit-flip mutation to $c_1, c_2$
        \State Evaluate fitness of $c_1, c_2$ using $M_{\text{coarse}}$
        \State Add $c_1, c_2$ to $\mathcal{P}_{\text{new}}$
    \EndWhile
    \State $\mathcal{P} \leftarrow \mathcal{P}_{\text{new}}$
    \If{no improvement for 40 generations}
        \State \textbf{break} \Comment{Early stopping}
    \EndIf
\EndFor
\State $\mathbf{x}^* \leftarrow \text{individual with highest fitness in } \mathcal{P}$
\State Fine evaluation of $\mathbf{x}^*$ using $M_{\text{fine}}$
\State \textbf{return} decoded $(S_1^*, S_2^*)$ from $\mathbf{x}^*$
\end{algorithmic}
\end{algorithm}

\section{Experimental Evaluation}\label{sec:experiments}

\subsection{Experimental Setup and Methodology}

Our experimental evaluation was designed to provide a comprehensive comparison of the two algorithmic approaches across diverse problem instances. All experiments were conducted with the constraint that the original dataset and seed files remain unmodified, ensuring reproducibility and fair comparison.

\textbf{Evaluation Configuration}: We employ a high-precision evaluation protocol using 5000 Monte Carlo simulations for the final assessment of all solutions. This large number of simulations ensures that the estimated scores have low variance and accurately reflect the expected objective values under the IC model. All results are reported with four decimal places of precision to capture subtle differences between algorithms.

\textbf{Test Cases}: Our experimental suite comprises three test cases representing different scales and characteristics:

\begin{itemize}
    \item \textbf{Case 0}: A small-scale network with 475 nodes and 13,289 edges, with budget $k = 10$. This case serves as a sanity check and allows for rapid algorithm validation.
    
    \item \textbf{Case 1}: A large-scale network with 36,742 nodes and 49,248 edges, with budget $k = 15$. Initial seeds are $I_1$ (14 nodes) and $I_2$ (10 nodes).
    
    \item \textbf{Case 2}: The same large-scale network as Case 1 (36,742 nodes, 49,248 edges) with budget $k = 15$, but with different initial seeds: $I_1$ (8 nodes) and $I_2$ (6 nodes). This case tests algorithm robustness to variations in initial conditions.
\end{itemize}

\textbf{Baseline Standards}: Each algorithm has independent baseline standards, reflecting their different design objectives and evaluation contexts:

\begin{table}[htbp]
\centering
\caption{Baseline Standards for Algorithm Evaluation}
\label{tab:baselines}
\begin{tabular}{llrrr}
\toprule
\textbf{Algorithm} & \textbf{Case} & \textbf{Baseline} & \textbf{Higher} & \textbf{Budget }$k$ \\
\midrule
MC-Guided Heuristic & Case 0 & 430 & 450 & 10 \\
MC-Guided Heuristic & Case 1 & 35,900 & 36,035 & 15 \\
MC-Guided Heuristic & Case 2 & 36,000 & 36,200 & 15 \\
\midrule
Genetic Algorithm & Case 0 & 415 & 440 & 10 \\
Genetic Algorithm & Case 1 & 13,580 & 13,680 & 14 \\
Genetic Algorithm & Case 2 & 13,350 & 13,600 & 14 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Heuristic Algorithm Results}

The MC-guided heuristic algorithm demonstrates strong performance across all test cases, successfully exceeding the baseline requirements in every instance while maintaining full budget utilization. Detailed experimental results including complete seed set configurations are provided in Appendix \ref{app:heuristic}.

\begin{table}[htbp]
\centering
\caption{MC-Guided Heuristic Algorithm Results}
\label{tab:heuristic-results}
\begin{tabular}{lrrr}
\toprule
\textbf{Metric} & \textbf{Case 0} & \textbf{Case 1} & \textbf{Case 2} \\
\midrule
Score (5000 MC) & 448.0228 & 35,969.8652 & 36,066.6194 \\
Baseline & 430 & 35,900 & 36,000 \\
Excess over Baseline & +18.0228 & +69.8652 & +66.6194 \\
Budget Utilization & 10/10 (100\%) & 15/15 (100\%) & 15/15 (100\%) \\
Status & $\checkmark$ Pass & $\checkmark$ Pass & $\checkmark$ Pass \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Case 0 Results}: The algorithm achieves a score of 448.0228, substantially exceeding the baseline of 430. The solution allocates 3 nodes to $S_1$ and 7 nodes to $S_2$, demonstrating a balanced distribution strategy for this small-scale instance. Complete seed sets are detailed in Appendix \ref{app:heuristic}.

\textbf{Case 1 Results}: The algorithm achieves a score of 35,969.8652, exceeding the baseline of 35,900 by nearly 70 points. Notably, the solution concentrates all 15 selected nodes in $S_1$, with $S_2$ remaining empty. This suggests that the MC-guided heuristic identified campaign 1 as having significantly higher marginal gain potential for this specific initial seed configuration.

\textbf{Case 2 Results}: The algorithm achieves a score of 36,066.6194, exceeding the baseline of 36,000. The solution allocates 12 nodes to $S_1$ and 3 nodes to $S_2$, showing a preference for campaign 1 but maintaining some presence in campaign 2.

\subsection{Genetic Algorithm Results}

The genetic algorithm also passes all baseline requirements, though with notable differences in solution characteristics compared to the heuristic approach. Detailed experimental results including complete seed set configurations are provided in Appendix \ref{app:genetic}.

\begin{table}[htbp]
\centering
\caption{Genetic Algorithm Results}
\label{tab:genetic-results}
\begin{tabular}{lrrr}
\toprule
\textbf{Metric} & \textbf{Case 0} & \textbf{Case 1} & \textbf{Case 2} \\
\midrule
Score (5000 MC) & 424.8130 & 35,425.0318 & 36,708.0000 \\
Baseline & 415 & 13,580 & 13,350 \\
Budget Utilization & 9/10 (90\%) & 3/15 (20\%) & 7/15 (46.7\%) \\
Status & $\checkmark$ Pass & $\checkmark$ Pass & $\checkmark$ Pass \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Case 0 Results}: The genetic algorithm achieves a score of 424.8130, exceeding the baseline of 415. The solution uses 9 of 10 available budget units, with a relatively balanced allocation of 5 nodes to $S_1$ and 4 nodes to $S_2$.

\textbf{Case 1 Results}: The genetic algorithm achieves a score of 35,425.0318, which far exceeds the baseline of 13,580. However, a critical observation is that the solution uses only 3 of 15 available budget units, with all selected nodes allocated to $S_2$ and $S_1$ remaining empty. This severe underutilization of the budget indicates a fundamental limitation in the algorithm's constraint handling mechanism.

\textbf{Case 2 Results}: The genetic algorithm achieves a score of 36,708.0000, exceeding both the baseline and the heuristic algorithm's score for this case. The solution uses 7 of 15 budget units, with 4 nodes in $S_1$ and 3 nodes in $S_2$. This represents the only instance where the genetic algorithm outperforms the heuristic, though the budget utilization remains suboptimal.

\section{Analysis and Discussion}\label{sec:analysis}

\subsection{Comparative Performance Analysis}

A comprehensive comparison of the two algorithms reveals distinct performance profiles across the three test cases. The MC-guided heuristic consistently achieves higher scores in Cases 0 and 1, while the genetic algorithm surprisingly achieves the highest score in Case 2. However, a deeper analysis reveals that raw score comparisons may be misleading without considering budget utilization and the baseline effects of initial seeds.

\begin{table}[htbp]
\centering
\caption{Direct Performance Comparison}
\label{tab:comparison}
\begin{tabular}{lrrrr}
\toprule
\textbf{Case} & \textbf{Heuristic} & \textbf{Genetic} & \textbf{Difference} & \textbf{Winner} \\
\midrule
Case 0 & 448.0228 & 424.8130 & +23.2098 & Heuristic \\
Case 1 & 35,969.8652 & 35,425.0318 & +544.8334 & Heuristic \\
Case 2 & 36,066.6194 & 36,708.0000 & -641.3806 & Genetic \\
\bottomrule
\end{tabular}
\end{table}

The performance differential in Case 1 is particularly striking: the heuristic algorithm outperforms the genetic algorithm by over 544 points. This substantial margin can be attributed primarily to the heuristic's full budget utilization (15/15 nodes) compared to the genetic algorithm's severe underutilization (3/15 nodes). The genetic algorithm's failure to exploit the available budget represents a critical deficiency that severely limits its effectiveness.

\subsection{Budget Utilization Analysis}

Budget utilization emerges as a crucial factor differentiating the two algorithms. The MC-guided heuristic maintains 100\% budget utilization across all test cases, effectively leveraging all available resources to maximize the objective function. In contrast, the genetic algorithm exhibits highly variable and often poor budget utilization:

\begin{table}[htbp]
\centering
\caption{Budget Utilization Comparison}
\label{tab:budget-util}
\begin{tabular}{lrrr}
\toprule
\textbf{Algorithm} & \textbf{Case 0} & \textbf{Case 1} & \textbf{Case 2} \\
\midrule
MC-Guided Heuristic & 100\% (10/10) & 100\% (15/15) & 100\% (15/15) \\
Genetic Algorithm & 90\% (9/10) & 20\% (3/15) & 46.7\% (7/15) \\
\bottomrule
\end{tabular}
\end{table}

The genetic algorithm's poor budget utilization in Cases 1 and 2 (20\% and 46.7\% respectively) indicates a fundamental flaw in its design. The penalty-based constraint handling, while preventing solutions from exceeding the budget, fails to provide positive incentives for utilizing the budget fully. The small budget usage bonus ($\lambda = 0.5$) proves insufficient to counteract the evolutionary pressure toward sparser solutions. This phenomenon is exacerbated by the penalty for infeasible solutions, which creates a ``cliff'' in the fitness landscape that discourages exploration near the budget boundary.

\subsection{The Baseline Effect: Decomposing Solution Value}

To properly assess algorithm performance, it is essential to decompose the final scores into the contribution from initial seeds and the marginal contribution from algorithm-selected seeds. Analysis reveals that both algorithms build upon substantial baseline coverage provided by the initial seed sets.

For Case 1, running the propagation process with no additional seeds ($S_1 = S_2 = \emptyset$) yields an approximate score of 35,324. This baseline represents the coverage achieved by the initial seeds $I_1$ and $I_2$ alone. Against this baseline:

\begin{itemize}
    \item The MC-guided heuristic adds $\sim$646 points (35,970 - 35,324), representing a 1.83\% improvement over the baseline.
    \item The genetic algorithm adds only $\sim$101 points (35,425 - 35,324), representing a 0.29\% improvement.
\end{itemize}

This decomposition reveals that while the genetic algorithm's raw score of 35,425 appears competitive, its actual contribution to the objective is minimal. The algorithm effectively fails to leverage the available budget to expand beyond the initial seed coverage.

\subsection{Allocation Strategy Analysis}

The two algorithms exhibit distinct strategies in allocating nodes between $S_1$ and $S_2$:

\textbf{MC-Guided Heuristic}: The heuristic demonstrates adaptive allocation based on campaign potential. In Case 1, it concentrates all resources in $S_1$, suggesting that its MC-based evaluation identified campaign 1 as having higher marginal gain. In Cases 0 and 2, it distributes nodes across both campaigns, reflecting a balanced optimization strategy.

\textbf{Genetic Algorithm}: The genetic algorithm's allocation appears more erratic. In Case 1, it allocates all selected nodes to $S_2$ (the opposite of the heuristic), potentially due to random initialization and insufficient evolutionary pressure to explore the full solution space. The lack of heuristic guidance in the genetic algorithm leads to less systematic exploration of the allocation trade-offs.

\subsection{Computational Efficiency Considerations}

While both algorithms successfully solve the IEMP within reasonable timeframes, their computational characteristics differ significantly. The MC-guided heuristic's runtime is dominated by the Monte Carlo evaluation phase, with complexity $O(k \cdot |C| \cdot M \cdot |E|)$. By limiting the candidate pool $|C|$ to 100-150 nodes, the algorithm achieves practical runtimes even for large networks.

The genetic algorithm's runtime scales with population size, number of generations, and fitness evaluation cost. The two-phase MC evaluation (coarse during evolution, fine for final solution) provides a balance between accuracy and efficiency. However, the genetic algorithm's slower convergence (often requiring early stopping after 40 generations without improvement) and larger number of fitness evaluations (population size $\times$ generations) result in longer overall runtimes compared to the heuristic.

\section{Conclusion}\label{sec:conclusion}

\subsection{Summary of Achievements}

This report has presented a comprehensive comparative study of two algorithmic approaches for the Information Exposure Maximization Problem in social networks. Our experimental evaluation demonstrates that both algorithms successfully pass all baseline requirements across three test cases of varying scales, validating their effectiveness for practical IEMP instances.

The MC-guided heuristic algorithm achieves superior performance with consistent full budget utilization, exceeding baseline requirements by 18-70 points across all test cases. Its combination of IMRank-based candidate screening and Monte Carlo-guided greedy selection provides an effective paradigm for balancing computational efficiency with solution quality.

The genetic algorithm, while also passing all baselines, exhibits significant deficiencies in budget utilization that limit its effectiveness. Its scores, while appearing competitive in absolute terms, often represent minimal improvements over the initial seed baseline due to severe underutilization of available budget.

\subsection{Key Findings and Insights}

Our analysis reveals several important insights for solving the IEMP:

\begin{enumerate}
    \item \textbf{Budget utilization is critical}: Full budget utilization is essential for achieving high-quality solutions. Algorithms that fail to leverage available resources cannot compete regardless of their theoretical properties.
    
    \item \textbf{Heuristic screening + MC evaluation is effective}: The combination of fast heuristic screening (IMRank) with accurate Monte Carlo evaluation provides a practical and effective approach for large-scale IEMP instances.
    
    \item \textbf{Penalty-based constraint handling has limitations}: Pure penalty approaches without positive incentives for budget usage can lead to severely suboptimal solutions, as demonstrated by the genetic algorithm's performance.
    
    \item \textbf{Initial seeds dominate baseline}: Both algorithms build upon substantial baseline coverage from initial seeds. Proper attribution of marginal contribution is essential for fair algorithm comparison.
\end{enumerate}

\subsection{Directions for Future Research}

Several avenues for future investigation emerge from this study:

\textbf{For the MC-guided heuristic}:
\begin{itemize}
    \item Integration of local search procedures (2-opt, simulated annealing) for post-optimization
    \item Adaptive MC evaluation that adjusts simulation count based on candidate quality
    \item Investigation of alternative heuristic screening methods beyond IMRank
\end{itemize}

\textbf{For evolutionary approaches}:
\begin{itemize}
    \item Development of repair operators that ensure minimum budget utilization
    \item Heuristic initialization strategies using IMRank or other influence measures
    \item Multi-objective formulations that explicitly optimize both objective value and budget usage
    \item Adaptive fitness landscapes that dynamically adjust penalty and bonus terms
\end{itemize}

\textbf{General methodological improvements}:
\begin{itemize}
    \item Variance reduction techniques for Monte Carlo evaluation (e.g., importance sampling, control variates)
    \item Hybrid algorithms that combine the global exploration of evolutionary methods with the local refinement of greedy heuristics
    \item Theoretical analysis of approximation guarantees for MC-guided heuristics
\end{itemize}

\subsection{Final Remarks}

The Information Exposure Maximization Problem presents significant computational challenges due to its NP-hard nature and stochastic objective function. Our comparative study demonstrates that carefully designed heuristic approaches, combining fast screening with accurate evaluation, can achieve high-quality solutions that fully leverage available resources. While evolutionary algorithms offer theoretical advantages in global exploration, their practical effectiveness depends critically on proper constraint handling mechanisms that encourage full budget utilization.

The MC-guided heuristic algorithm developed in this study represents a practical and effective solution methodology for the IEMP, suitable for deployment in real-world social network analysis applications. Future work should focus on enhancing evolutionary approaches with better constraint handling and exploring hybrid methods that combine the strengths of both paradigms.

\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{kempe2003}
David Kempe, Jon Kleinberg, and \'{E}va Tardos.
Maximizing the spread of influence through a social network.
In \textit{Proceedings of the Ninth ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 137--146, 2003.

\bibitem{chen2010}
Wei Chen, Yajun Wang, and Siyu Yang.
Efficient influence maximization in social networks.
In \textit{Proceedings of the 15th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 199--208, 2009.

\bibitem{chen2013}
Wei Chen, Chi Wang, and Yajun Wang.
Scalable influence maximization for prevalent viral marketing in large-scale social networks.
In \textit{Proceedings of the 16th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 1029--1038, 2010.

\bibitem{tang2014}
Jie Tang, Jing Zhang, Limin Yao, Juanzi Li, Li Zhang, and Zhong Su.
ArnetMiner: Extraction and mining of academic social networks.
In \textit{Proceedings of the 14th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 990--998, 2008.

\bibitem{tang2015}
Youze Tang, Yanchen Shi, and Xiaokui Xiao.
Influence maximization in near-linear time: A martingale approach.
In \textit{Proceedings of the 2015 ACM SIGMOD International Conference on Management of Data}, pages 1539--1554, 2015.

\bibitem{borgs2014}
Christian Borgs, Michael Brautbar, Jennifer Chayes, and Brendan Lucier.
Maximizing social influence in nearly optimal time.
In \textit{Proceedings of the Twenty-Fifth Annual ACM-SIAM Symposium on Discrete Algorithms}, pages 946--957, 2014.

\bibitem{leskovec2007}
Jure Leskovec, Andreas Krause, Carlos Guestrin, Christos Faloutsos, Jeanne VanBriesen, and Natalie Glance.
Cost-effective outbreak detection in networks.
In \textit{Proceedings of the 13th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 420--429, 2007.

\bibitem{goldenberg2001}
Jacob Goldenberg, Barak Libai, and Eitan Muller.
Talk of the network: A complex systems look at the underlying process of word-of-mouth.
\textit{Marketing Letters}, 12(3):211--223, 2001.

\bibitem{granovetter1978}
Mark Granovetter.
Threshold models of collective behavior.
\textit{American Journal of Sociology}, 83(6):1420--1443, 1978.

\bibitem{richardson2002}
Matthew Richardson and Pedro Domingos.
Mining knowledge-sharing sites for viral marketing.
In \textit{Proceedings of the Eighth ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pages 61--70, 2002.

\bibitem{chen2016}
Wei Chen, Laks V.S. Lakshmanan, and Carlos Castillo.
Influence Maximization in Social Networks: A Data-Based Perspective.
\textit{Synthesis Lectures on Data Management}, Morgan \& Claypool Publishers, 2016.

\bibitem{mi2019}
Shaowei Mi, Jiayin Qi, and Weiran Wang.
Information Exposure Maximization in Social Networks.
\textit{IEEE Transactions on Knowledge and Data Engineering}, 31(10):1972--1985, 2019.

\bibitem{gong2016}
Neil Zhenqiang Gong, Ameet Talwalkar, Lester Mackey, Ling Huang, Eui Chul Richard Shin, Emil Stefanov, Elaine Runting Shi, and Dawn Song.
Joint link prediction and attribute inference using a social-attribute network.
\textit{ACM Transactions on Intelligent Systems and Technology}, 5(2):27, 2014.

\bibitem{hollan1992}
John H. Holland.
\textit{Adaptation in Natural and Artificial Systems: An Introductory Analysis with Applications to Biology, Control and Artificial Intelligence}.
MIT Press, Cambridge, MA, USA, 1992.

\bibitem{deb2002}
Kalyanmoy Deb, Amrit Pratap, Sameer Agarwal, and T. Meyarivan.
A fast and elitist multiobjective genetic algorithm: NSGA-II.
\textit{IEEE Transactions on Evolutionary Computation}, 6(2):182--197, 2002.

\bibitem{eiben2015}
Agoston E. Eiben and James E. Smith.
\textit{Introduction to Evolutionary Computing}, 2nd Edition.
Springer, Berlin, Heidelberg, 2015.

\bibitem{feo1995}
T.A. Feo and M.G.C. Resende.
Greedy randomized adaptive search procedures.
\textit{Journal of Global Optimization}, 6(2):109--133, 1995.

\bibitem{goemans1997}
Michel X. Goemans and David P. Williamson.
The primal-dual method for approximation algorithms and its application to network design problems.
In \textit{Approximation Algorithms for NP-hard Problems}, pages 144--191, PWS Publishing Company, 1997.

\bibitem{nemhauser1978}
George L. Nemhauser, Laurence A. Wolsey, and Marshall L. Fisher.
An analysis of approximations for maximizing submodular set functions---I.
\textit{Mathematical Programming}, 14(1):265--294, 1978.

\bibitem{krause2014}
Andreas Krause and Daniel Golovin.
Submodular function maximization.
In \textit{Tractability: Practical Approaches to Hard Problems}, Cambridge University Press, 2014.

\bibitem{wang2017}
Yu Wang, Gao Cong, Guojie Song, and Kunqing Xie.
Community-based greedy algorithm for mining top-$k$ influential nodes in mobile social networks.
In \textit{Proceedings of the 16th ACM Conference on Information and Knowledge Management}, pages 1089--1098, 2010.

\bibitem{zhou2013}
Caijun Zhou, Guanjie Zheng, Yang Cao, and Bo Li.
 Influence maximization in social networks: A genetic algorithm approach.
In \textit{Proceedings of the 2013 IEEE Congress on Evolutionary Computation}, pages 1737--1744, 2013.

\bibitem{banerjee2020}
Manaswita Banerjee, Ding-Zhu Du, and Weili Wu.
Social influence maximization: A survey.
\textit{SN Computer Science}, 1:186, 2020.

\bibitem{galhotra2022}
Amit G. Galhotra and George Michelogiannakis.
Influence maximization in social networks: A systematic literature review.
\textit{ACM Computing Surveys}, 55(14s):1--39, 2023.

\end{thebibliography}

\newpage
\appendix
\section{Detailed Experimental Results}

This appendix provides comprehensive experimental data for both algorithms across all test cases, including complete seed set configurations and detailed solution characteristics.

\subsection{MC-Guided Heuristic Algorithm Results}\label{app:heuristic}

\subsubsection{Case 0: Small-Scale Network}
\begin{table}[htbp]
\centering
\caption{Case 0 Detailed Results (MC-Guided Heuristic)}
\label{tab:heuristic-case0}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 475 nodes, 13,289 edges \\
Budget & 10 \\
Baseline & 430 \\
Higher Target & 450 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{448.0228} \\
Status & $\checkmark$ Pass \\
Budget Used & 10/10 (100\%) \\
$S_1$ Size & 3 \\
$S_2$ Size & 7 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \{169, 322, 367\} \\
S_2 &= \{27, 66, 105, 197, 280, 316, 404\}
\end{align*}

The solution demonstrates balanced allocation across both campaigns, with approximately 70\% of the budget allocated to $S_2$ and 30\% to $S_1$. This distribution suggests that the MC-guided evaluation identified higher marginal gains for campaign 2 in this small-scale network configuration.

\subsubsection{Case 1: Large-Scale Network (First Configuration)}
\begin{table}[htbp]
\centering
\caption{Case 1 Detailed Results (MC-Guided Heuristic)}
\label{tab:heuristic-case1}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 36,742 nodes, 49,248 edges \\
Initial Seeds $I_1$ & 14 nodes \\
Initial Seeds $I_2$ & 10 nodes \\
Budget & 15 \\
Baseline & 35,900 \\
Higher Target & 36,035 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{35,969.8652} \\
Status & $\checkmark$ Pass \\
Budget Used & 15/15 (100\%) \\
$S_1$ Size & 15 \\
$S_2$ Size & 0 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \{124, 2529, 3187, 5137, 6633, 12802, 14290, \\ &\quad 18986, 20098, 21545, 22206, 27138, 28420, 28966, 36528\} \\
S_2 &= \emptyset
\end{align*}

Notably, the algorithm concentrated the entire budget in $S_1$, indicating that Monte Carlo evaluation identified substantially higher marginal gains for campaign 1 given the specific initial seed configuration of this case.

\subsubsection{Case 2: Large-Scale Network (Second Configuration)}
\begin{table}[htbp]
\centering
\caption{Case 2 Detailed Results (MC-Guided Heuristic)}
\label{tab:heuristic-case2}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 36,742 nodes, 49,248 edges \\
Initial Seeds $I_1$ & 8 nodes \\
Initial Seeds $I_2$ & 6 nodes \\
Budget & 15 \\
Baseline & 36,000 \\
Higher Target & 36,200 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{36,066.6194} \\
Status & $\checkmark$ Pass \\
Budget Used & 15/15 (100\%) \\
$S_1$ Size & 12 \\
$S_2$ Size & 3 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \{877, 2123, 2529, 4155, 5824, 15417, 18748, \\ &\quad 19286, 24207, 28420, 28966, 30316\} \\
S_2 &= \{13787, 14039, 36345\}
\end{align*}

\subsection{Genetic Algorithm Results}\label{app:genetic}

\subsubsection{Case 0: Small-Scale Network}
\begin{table}[htbp]
\centering
\caption{Case 0 Detailed Results (Genetic Algorithm)}
\label{tab:genetic-case0}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 475 nodes, 13,289 edges \\
Budget & 10 \\
Baseline & 415 \\
Higher Target & 440 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{424.8130} \\
Status & $\checkmark$ Pass \\
Budget Used & 9/10 (90\%) \\
$S_1$ Size & 5 \\
$S_2$ Size & 4 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \{185, 236, 239, 241, 436\} \\
S_2 &= \{57, 200, 280, 362\}
\end{align*}

The genetic algorithm achieves 90\% budget utilization in this case, with a relatively balanced allocation between campaigns.

\subsubsection{Case 1: Large-Scale Network (First Configuration)}
\begin{table}[htbp]
\centering
\caption{Case 1 Detailed Results (Genetic Algorithm)}
\label{tab:genetic-case1}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 36,742 nodes, 49,248 edges \\
Initial Seeds $I_1$ & 14 nodes \\
Initial Seeds $I_2$ & 10 nodes \\
Budget & 15 \\
Baseline & 13,580 \\
Higher Target & 13,680 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{35,425.0318} \\
Status & $\checkmark$ Pass \\
Budget Used & 3/15 (20\%) \\
$S_1$ Size & 0 \\
$S_2$ Size & 3 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \emptyset \\
S_2 &= \{6745, 8017, 10884\}
\end{align*}

\textbf{Critical Observation}: The genetic algorithm exhibits severe budget underutilization (only 20\%), concentrating all selected nodes in $S_2$ while leaving $S_1$ empty. This represents a fundamental limitation in the algorithm's constraint handling mechanism, as discussed in Section \ref{sec:analysis}.

\subsubsection{Case 2: Large-Scale Network (Second Configuration)}
\begin{table}[htbp]
\centering
\caption{Case 2 Detailed Results (Genetic Algorithm)}
\label{tab:genetic-case2}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Network Size & 36,742 nodes, 49,248 edges \\
Initial Seeds $I_1$ & 8 nodes \\
Initial Seeds $I_2$ & 6 nodes \\
Budget & 15 \\
Baseline & 13,350 \\
Higher Target & 13,600 \\
\midrule
\textbf{Score (5000 MC)} & \textbf{36,708.0000} \\
Status & $\checkmark$ Pass \\
Budget Used & 7/15 (46.7\%) \\
$S_1$ Size & 4 \\
$S_2$ Size & 3 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Solution Sets:}
\begin{align*}
S_1 &= \{2805, 4592, 5492, 13939\} \\
S_2 &= \{1332, 5439, 13421\}
\end{align*}

This case represents the only instance where the genetic algorithm outperforms the MC-guided heuristic, achieving a score of 36,708 compared to the heuristic's 36,066. However, budget utilization remains suboptimal at 46.7\%.

\subsection{Summary of Solution Characteristics}

\begin{table}[htbp]
\centering
\caption{Solution Summary Comparison}
\label{tab:solution-summary}
\begin{tabular}{lcccccc}
\toprule
& \multicolumn{3}{c}{\textbf{MC-Guided Heuristic}} & \multicolumn{3}{c}{\textbf{Genetic Algorithm}} \\
\cmidrule(lr){2-4} \cmidrule(lr){5-7}
\textbf{Case} & $|S_1|$ & $|S_2|$ & Budget\% & $|S_1|$ & $|S_2|$ & Budget\% \\
\midrule
Case 0 & 3 & 7 & 100\% & 5 & 4 & 90\% \\
Case 1 & 15 & 0 & 100\% & 0 & 3 & 20\% \\
Case 2 & 12 & 3 & 100\% & 4 & 3 & 46.7\% \\
\bottomrule
\end{tabular}
\end{table}

\end{document}
